Predictors of frog survival following translocations - create dataset

### 2022-10-27 code/translocation_survival_createdata.Rmd
Add column descriptions

>>>>

### Description of dataset columns
- site_id: Unique 5-digit site identifier.
- elevation: Elevation of site above sea level (in meters). Obtained from 7.5' USGS topographic maps. 
- shore: Complex shoreline habitats (boulders, overhanging banks, rock crevices) available to frogs during winter, or not present and/or unavailable due to reduction in water level (1 or 0, respectively). 
- snow_t: April 1 snow water equivalent (SWE) in year of translocation, measured at Dana Meadows (DAN station).
- snow_t1: April 1 snow water equivalent (SWE) in year following translocation, measured at Dana Meadows (DAN station).
- date: Date of translocation (yyyy-mm-dd).
- year: Year of translocation.
- day: Day of year on which translocation occurred, expressed as number of days since 01-January.  
- order: Order of translocation at the site. 1 = first translocation, 2 = second translocation, etc.
- pit_tag_ref: Unique 9 or 15-digit PIT tag identifier.  
- donor: Unique 5-digit identifier of donor site at which frogs were collected. 
- sex: Sex of translocated frog. 
- length: Snout-vent length of translocated frog, measured at donor site at time of capture and $\leq$ 24 hours before translocation (in millimeters).
- weight: Weight of translocated frog, measured at donor site at time of capture and $\leq$ 24 hours before translocation (in grams).
- bd_load: Bd infection intensity, measured at donor site at time of capture and $\leq$ 24 hours before translocation (ITS1 copies * 80).
- survival: Probability of surviving one year after translocation.
